Spatial modelling of the two-party preferred vote in Australian federal elections: 2001--2016

### 2020-04-07 submission_070420/anzjs_elections.tex
Files as submitted in final submission

\caption{Partial residual plots by election year for a selection of predictors. Linear model with 95\% confidence bands overlaid. Several predictors had a negative relationship: with larger values indicating the electorate more likely preferenced Labor. Most relationships were relatively stable over elections, except \texttt{Unemployment} and \texttt{Education}.}\label{fig:partresplot2}
\end{figure}

@@

From 2007 onwards, proportions of both marriages (\texttt{Married}) and de facto relationships (\texttt{DeFacto}) were found to be strong predictors of the two-party preferred vote in favour of the Labor party. In 2001 and 2004 neither of these variables were significant (see rows 4 and 5 in Figure \ref{fig:partresplot2}).

@@

It is often hypothesised that states have a systematic bias towards one of the two major parties. Boxplots of residuals grouped by state (Figure \ref{fig:resstate}) showed that the data reflects this to only a limited extent. Tasmania and the Australian Capital Territory appeared to have a bias towards Labor, whereas the South Australia and the Northern Territory tended towards voting Liberal. However, there were relatively few electorates in each of these states (five, two, eleven and two respectively), so this apparent result may be due to incumbent effects rather than an actual state-specific bias.

>>>>

\caption{Partial residual plots by election year for a selection of predictors. Linear model with 95\% confidence bands overlaid. Several predictors had a negative relationship: the larger the value the more likely the electorate preferenced Labor. Most relationships were relatively stable over elections, except \texttt{Unemployment} and \texttt{Education}.}\label{fig:partresplot2}
\end{figure}

@@

From 2007 onwards, the percentage of people in both marriages (\texttt{Married}) and de facto relationships (\texttt{DeFacto}) were found to be strong predictors of the two-party preferred vote in favour of the Labor party. In 2001 and 2004 neither of these variables were significant (see rows 4 and 5 in Figure \ref{fig:partresplot2}).

@@

It is often hypothesised that states have had a systematic bias towards one of the two major parties. Boxplots of residuals grouped by state (Figure \ref{fig:resstate}) showed that the data reflects this to only a limited extent. Tasmania and the Australian Capital Territory appeared to have a bias towards Labor, whereas the South Australia and the Northern Territory tended towards voting Liberal. However, there were relatively few electorates in each of these states (five, two, eleven and two respectively), so this apparent result may be due to incumbent effects rather than an actual state-specific bias.
